Depression and suicidality as costly signals of need

### 2021-03-22 Paper.rmd
Added histograms. Tweaked a few other plots.

@@

```{r mentallyill, fig.width=8, fig.cap="Proportion of participants in each condition who thought that the vignette victim was mentally ill. Means estimated with a generalized linear regression model with the quasibinomial family."}
effectsPlots$m21plot
```

>>>>

## Distributions of T2 Belief and Action by signal and vignette

```{r distbelief, fig.width=10, fig.height=10, fig.cap="Histograms of T2 Belief by signal and vignette."}
ggplot(d, aes(x = T2Belief, fill=signal)) +
  geom_histogram(colour='grey') +
  scale_x_continuous(breaks = c(0, 0.5, 1)) +
  facet_grid(vignette~signal) +
  guides(fill='none') +
  xlab('\n T2 Belief') +
  theme_minimal(15) + 
  theme(strip.text.y = element_text(angle=0, hjust=0))
```

```{r distaction, fig.width=10, fig.height=10, fig.cap="Histograms of T2 Action by signal and vignette."}
ggplot(d, aes(x = T2Action, fill=signal)) +
  geom_histogram(colour='grey') +
  scale_x_continuous(breaks = c(0, 0.5, 1)) +
  facet_grid(vignette~signal) +
  guides(fill='none') +  
  xlab('\n T2 Action') +
  theme_minimal(15) + 
  theme(strip.text.y = element_text(angle=0, hjust=0))
```

@@

```{r mentallyillT1, fig.width=8, fig.cap="Proportion of participants in each vignette who thought that the victim was mentally ill at T1. Means estimated with a generalized linear regression model with the quasibinomial family."}
effectsPlots$m27plot + ggtitle('Time 1')
```

```{r mentallyillT2, fig.width=8, fig.cap="Proportion of participants in each condition who thought that the victim was mentally ill at T2, controlling for perceptions of mental illness at T1. Means estimated with a generalized linear regression model with the quasibinomial family."}
effectsPlots$m21plot + ggtitle('Time 2')
```
